experDesign: helping performing experiments on batches

### 2021-04-16 paper.Rmd
Some more tweaks

For completeness a description of the usage of the different software

```{r example-data}
data(survey, package = "MASS")
survey$ID <- seq_len(nrow(survey))
VoI <- c("Sex", "Smoke", "Age")
n_batch <- 3
iterations <- 1000
```

@@

OSAT provides some template for some setups:

```{r osat}
library("OSAT")
gs <- setup.sample(survey, optimal = VoI)
gc <- setup.container(IlluminaBeadChip96Plate, n_batch, batch = 'plates')
gSetup <- create.optimized.setup(sample = gs, container = gc, nSim = iterations)
```

@@

```{r anticlust}
library("anticlust")
anticlust_index <- anticlustering(
  survey[, VoI],
  K = n_batch,
  objective = "variance",
  method = "exchange",
  repetitions = iterations
)
```

@@

```{r Omixer}
library("Omixer")
layout <- data.frame(well = 1:96, 
    row = factor(rep(1:8, each=12), labels = LETTERS[1:8]),
    column = rep(1:12, 8), 
    plate  = 1,
    chip = as.integer(ceiling(rep(1:12, 8)/2)))
layout$chipPos <- ifelse(layout$column %% 2 == 0, 
                         as.numeric(layout$row) + 8,
                         layout$row)
layout2 <- layout
layout2$plate <- 2
layout3 <- layout
layout3$plate <- 3
plates <- rbind(layout, layout2, layout3)
Omixer_index <- omixerRand(survey, sampleId = "ID", 
    block = "block", iterNum = 10, wells = 96,
    plateNum = n_batch, randVars = VoI, layout = plates, techVars = NULL)
```

@@

```{r experDesign}
library("experDesign")
experDesign_index <- design(survey[, VoI], size_subset = 96,
                  iterations = iterations)
```

>>>>

For completeness a brief examples using each different software.

First of all a brief data setup.

```{r example-data}
data(cats, package = "MASS")
cats$ID <- seq_len(nrow(cats))
VoI <- c("Sex", "Bwt", "Hwt")
n_batch <- 2
iterations <- 10000
```

The objective is to group the cats in 2 groups to avoid any batch effect on further measures on them.
We set 10000 iterations and 2 groups

@@

OSAT provides some template for some layouts:

```{r osat}
library("OSAT")
gs <- setup.sample(cats, optimal = VoI)
gc <- setup.container(IlluminaBeadChip96Plate, n = n_batch, batch = 'plates')
gSetup <- create.optimized.setup(sample = gs, container = gc, nSim = iterations)
```

@@

anticlust only works with numeric variables:

```{r anticlust}
library("anticlust")
anticlust_index <- anticlustering(
  cats[, VoI],
  K = n_batch,
  objective = "variance",
  method = "exchange",
  repetitions = iterations
)
anticlust_index <- anticlustering(
  cats[, c("Bwt", "Hwt")],
  K = n_batch,
  objective = "variance",
  method = "exchange",
  repetitions = iterations
)
```

@@

```{r Omixer}
library("Omixer")
layout <- data.frame(well = 1:96, 
    row = factor(rep(1:8, each=12), labels = LETTERS[1:8]),
    column = rep(1:12, 8), 
    plate  = 1,
    chip = as.integer(ceiling(rep(1:12, 8)/2)))
layout$chipPos <- ifelse(layout$column %% 2 == 0, 
                         as.numeric(layout$row) + 8,
                         layout$row)
layout2 <- layout
layout2$plate <- 2
plates <- rbind(layout, layout2)
Omixer_index <- omixerRand(cats, sampleId = "ID", 
    block = "none", iterNum = iterations, wells = 96,
    plateNum = n_batch, randVars = VoI, layout = plates, techVars = NULL)
```

@@

```{r experDesign}
library("experDesign")
experDesign_index <- design(cats[, VoI], size_subset = 96,
                  iterations = iterations)
```

## Summary

Last we can compare some of the solutions

```{r compare}
OSAT_index <- get.experiment.setup(gSetup)$plates
table(batch_names(experDesign_index), anticlust_index)

table(batch_names(experDesign_index), OSAT_index)
table(anticlust_index, OSAT_index)
```

It doesn't seem possible to run Omixer without any spatial batch effect
